Technical Report

### 2018-06-27 fully-abstract-comp/technical-report.tex
Discharge a simple TODO.
Simplify xReadCond (thanks to the padding) and prove some results about splicing.

\begin{lemma}[Untrusted is trusted]
  \label{lem:untrusted-supset-trust}
  \begin{itemize}
  \item $\lrvtrusted(W) \supseteq \lrv(W)$
  \item $\lrrtrusted(W) \supseteq \lrr(W)$
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}

@@

\[
  \readCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad (\lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1) \wedge\\
      \qquad \forall r \in S \ldotp \pwheap(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions. Check whether needed for the stack condition.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \forall r \in S \ldotp |R(r)| = 1\\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge \\
      \qquad \forall r \in S \ldotp \pwfree(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\normal, \pwheap} \ldotp \\
      \quad \exists M : S \fun \powerset{\MemSeg} \\
      \qquad \biguplus_{r\in S} \dom(M(r)) \supseteq A \wedge\\
      % \qquad \biguplus_{r\in S} R(r) \# \biguplus_{r\in S} C(r) \wedge \\
      \qquad \forall r \in S \ldotp \pwheap(r) \nequal \codereg{\_,\_,M(r),\gc}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions.}

@@

\begin{lemma}[permission-based conditions shrinkable]
  \label{lem:conds-shrinkable}
  \begin{itemize}
  \item If $\npair{A} \in \readCond{\lin,W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \readCond{\lin,W}$.
  \item If $\npair{A} \in \writeCond{\lin,W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \writeCond{\lin,W}$.
  \item If $\npair{A} \in \xReadCond{W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \xReadCond{W}$.
  \item If $\npair{A} \in \execCond{W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \execCond{W}$.
  \end{itemize}
\end{lemma}
\begin{proof}
  Follows easily from the definitions.
  In the case for $\execCond{}$ where $\lin = \linear$, we have a partition of the world into $W = \oplus_{a \in A} W_a(a)$ that we need to convert into a partition $W = \oplus_{a \in A'} W_a'(a)$.
  It suffices construct new $W_a'$ by taking $W_a$ but adding $\oplus_{a\in(A\setminus A')}$ to an $W_a(a)$ for an arbitrary $a \in A'$ to make this work.
\end{proof}

@@

>>>>

\begin{lemma}[Untrusted is trusted]
  \label{lem:untrusted-supset-trust}
  \begin{itemize}
  \item $\lrvtrusted(W) \supseteq \lrv(W)$
  \item $\lrrtrusted(W) \supseteq \lrr(W)$
  \end{itemize}
\end{lemma}
\begin{proof}
  Follows easily by definition.
\end{proof}

@@

\[
  \readCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad (\lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1) \wedge\\
      \qquad \forall r \in S \ldotp \pwheap(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions. Check whether needed for the stack condition.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \forall r \in S \ldotp |R(r)| = 1\\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge \\
      \qquad \forall r \in S \ldotp \pwfree(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\normal, \pwheap} \ldotp \\
      \qquad \pwheap(r) \nequal \codereg{\_,\_,\code,\gc}\wedge\\
      \qquad \dom(\code) \supseteq A 
    \end{array}
  \right\}
\]

@@

\begin{lemma}[permission-based conditions shrinkable]
  \label{lem:conds-shrinkable}
  \begin{itemize}
  \item If $\npair{A} \in \readCond{\lin,W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \readCond{\lin,W}$.
  \item If $\npair{A} \in \writeCond{\lin,W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \writeCond{\lin,W}$.
  \item If $\npair{A} \in \xReadCond{W}$  and $A' \subseteq A$, then
    $\npair{A'} \in \xReadCond{W}$.
  \item If $\npair{A} \in \execCond{W}$  and $\emptyset \neq A' \subseteq A$, then
    $\npair{A'} \in \execCond{W}$.
  \end{itemize}
\end{lemma}
\begin{proof}
  Follows easily from the definitions.
  In the case for $\execCond{}$ where $\lin = \linear$, we have a partition of the world into $W = \oplus_{a \in A} W_a(a)$ that we need to convert into a partition $W = \oplus_{a \in A'} W_a'(a)$.
  It suffices construct new $W_a'$ by taking $W_a$ but adding $\oplus_{a\in(A\setminus A')}$ to an $W_a(a)$ for an arbitrary $a \in A'$ to make this work.
\end{proof}

@@

\begin{lemma}[permission-based conditions splicable]
  \label{lem:conds-splicable}
  If
  \begin{itemize}
  \item $[\baddr,\eaddr] = [\baddr_1,\eaddr_1] \uplus [\baddr_2,\eaddr_2]$
  \item $[\baddr,\eaddr]\mathrel{\#} \ta$
  \item $W_1\oplus W_2$ is defined.
  \end{itemize}
  then
  \begin{itemize}
  \item If $\npair{[\baddr_1,\eaddr_1]} \in \readCond{\lin,W_1}$ and $\npair{[\baddr_2,\eaddr_2]} \in \readCond{\lin,W_2}$, then $\npair{[\baddr,\eaddr]} \in \readCond{\lin,W_1 \oplus W_2}$
  \item If $\npair{[\baddr_1,\eaddr_1]} \in \writeCond{\lin,W_1}$ and $\npair{[\baddr_2,\eaddr_2]} \in \writeCond{\lin,W_2}$, then $\npair{[\baddr,\eaddr]} \in \writeCond{\lin,W_1 \oplus W_2}$.
  \item If $\npair{[\baddr_1,\eaddr_1]} \in \execCond{W_1}$ and $\npair{[\baddr_2,\eaddr_2]} \in \execCond{W_2}$, then $\npair{[\baddr,\eaddr]} \in \execCond{W_1 \oplus W_2}$.
  \end{itemize}

  If
  \begin{itemize}
  \item $[\baddr,\eaddr] = [\baddr_1,\eaddr_1] \uplus [\baddr_2,\eaddr_2]$
  \item $W_1\oplus W_2 \oplus W_M$ is defined.
  \item $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$
  \end{itemize}
  then
  \begin{itemize}
  \item If $\npair{[\baddr_1,\eaddr_1]} \in \xReadCond{\lin,W_1}$ and
    $\npair{[\baddr_2,\eaddr_2]} \in \xReadCond{\lin,W_2}$, then
    $\npair{[\baddr,\eaddr]} \in \xReadCond{\lin,W_1 \oplus W_2}$
  \end{itemize}

  If $[\baddr,\eaddr] = [\baddr_1,\eaddr_1] \uplus [\baddr_2,\eaddr_2]$, then
  \begin{itemize}
  \item If $\npair{[\baddr_1,\eaddr_1]} \in \stackReadCond{W_1}$ and $\npair{[\baddr_2,\eaddr_2]} \in \stackReadCond{W_2}$, then $\npair{[\baddr,\eaddr]} \in \stackReadCond{W_1 \oplus W_2}$
  \item If $\npair{[\baddr_1,\eaddr_1]} \in \stackWriteCond{W_1}$ and $\npair{[\baddr_2,\eaddr_2]} \in \stackWriteCond{W_2}$, then $\npair{[\baddr,\eaddr]} \in \stackWriteCond{W_1 \oplus W_2}$.
  \end{itemize}
\end{lemma}
\begin{proof}
  The results for $\readCond{}$, $\writeCond{}$, $\stackReadCond{}$ and $\stackWriteCond{}$ follow by taking the union of the two sets $S$, and the union of $R$ for every $r$.

  The result for $\execCond{}$ follows easily by definition and using Lemmas~\ref{lem:purePart-oplus} and~\ref{lem:oplus-future}.

  For $\xReadCond{}$, we get $r_i \in \addressable{\normal,W_i}$ such that $\pwheap[W_i](r_i) \nequal \codereg{\_,\_,\code_i,\gc}$ such that $\dom(\code_i)\supseteq [\baddr_i,\eaddr_i]$.
  From $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$, it follows that $\code_i = [\baddr_i',\eaddr_i']$ and if $r_1 \neq r_2$, then $[\baddr_1'-1,\eaddr_1+1] \mathrel{\#} [\baddr_2'-1,\eaddr_2'+1]$.
  Because $[\baddr,\eaddr] = [\baddr_1,\eaddr_1] \uplus [\baddr_2,\eaddr_2]$ and $[\baddr_i',\eaddr_i'] = \dom(\code_i)\supseteq [\baddr_i,\eaddr_i]$, we can derive that $r_1= r_2$.
  The result then follows by definition of $\xReadCond{}$.
\end{proof}
